In the following we will always work in atomic units. This entails setting four fundamental constants to the numeric value of 1
\begin{align*}
    \hbar = e = m_e = k_e = 1,
\end{align*}
where $\hbar$ is the reduced Planck constant, $e$ the elementary charge, $m_e$ the electron mass and $k_e$ the Coulomb constant being the inverse of a factor $4\pi$ multiplied with the permittivity in vacuum.  All quantities expressed are understood to be in atomic units, meaning that to convert values to more common sets of units, factors has to be included based on dimensional analysis of the respective quantity. Importantly we note energy, where one atomic unit is equal to $ 27.2113\ldots\text{ eV}$ and frequency $4.1341\ldots \cdot 10^{16} \text{ Hz}$

\subsection{Mathematical Framework and Notation}
In the following we will use the occupation representation, making use of creation $\crta{p}$ and annihilation $\ania{p}$ operators. As a shorthand, we will write $\crt{p} \equiv \crta{p}$ and $\ani{p} \equiv \ania{p}$ when no confusion can be made. $N$ represents the number of occupied states while $L$ the total number of states in our calculations. The indicies $p,q,\ldots$ are reserved for the $L$ general states, the $N$ occupied states are indexed by $i,j,\ldots$, while the $M \equiv L-N$ unoccupied (virtual) states by $a,b,\ldots$ indicies.

Since we are treating fermionic systems, the canonical anticommutation relations (CAR) are used

\begin{align*}
    \set{\crt{p},\crt{q}} = \set{\ani{p},\ani{q}} = 0 \hspace{20px} \set{\crt{p},\ani{q}} = \delta_{pq}.
\end{align*}
One and two body matrix elements are calculated using a computational basis, with explicit expressions for one body Hamiltonians $h(\vec{x})$ and two body interaction $v(\vec{x}, \vec{x}')$ here presented in position space

\begin{align*}
    \bra{p}\hat{h}\ket{q} &= \int \dd{\vec{x}} \psi_p^*(x) \hat{h}(\vec{x}) \psi_q(x) \\
    \elm{pq}{rs} &= \int \dd{\vec{x}}\dd{\vec{x}'} \psi_p^*(\vec{x})\psi_q^*(\vec{x}') \hat{v}(\vec{x},\vec{x}') \psi_r(\vec{x})\psi_s(\vec{x}')
\end{align*}
with $\psi_p$ being a single particle wave function, often chosen to be the eigenfunction of $\hat{h}$. Note that $p$ also contain the spin quantum number, meaning that $\dd \vec{x}$ implicitly contains a spin component. If $\hat{h}$ or $\hat{v}$ is spin \textit{independent}, this simply reduces to Kronecker deltas for the spin component. By swapping variables in the integral, we find a symmetry for the two-body matrix elements
\begin{align}
    \elm{pq}{rs} = \elm{qp}{sr}. \label[eq]{eq:theo:matrix_elements_symmetry}
\end{align}

It is often convenient to use antisymmetrized matrix elements, defined as 
\begin{align*}
    \elmAS{pq}{rs} = \elm{pq}{rs} - \elm{pq}{sr},
\end{align*}
where the terms are often referred to the \textit{direct} and \textit{exchange} terms respectively. Using the symmetry of \cref{eq:theo:matrix_elements_symmetry}, we find an expand symmetry for the antisymmetrized matrix elements

\begin{align}
    \elmAS{pq}{rs} = -\elmAS{pq}{sr} = -\elmAS{qp}{rs} = \elmAS{qp}{sr}. \label[eq]{eq:theo:matrix_elements_symmetry_AS}
\end{align}
The shorthands $\hshort{p}{q} \equiv \bra{p} \hat{h} \ket{q}$, $\elmshort{pq}{rs} \equiv \elm{pq}{rs}$ and $\elmASshort{pq}{rs} \equiv \elmAS{pq}{rs}$ will often be used. Using this formulation, a general two-body operator can be constructed
\begin{align}
    \ham = \sum_{pq} \hshort{p}{q}\crt{p}\ani{q} + \frac{1}{4} \sum_{pqrs} \elmASshort{pq}{rs}\crt{p}\crt{q}\ani{s}\ani{r} \label[eq]{eq:theo:second_quant_ham}
\end{align}
The simplest ground state ansatz
\begin{align*}
    \ketansatz = \crt{i}\crt{j}\ldots \ket{0},
\end{align*}
can be evaluated to calculate the simplest energy estimate using \text{Wicks Theorem} \citep{molinariNotesWickTheorem2017} 
\begin{align}
    \braansatz \ham \ketansatz = \sum_{i} \hshort{i}{i} + \frac{1}{2}\sum_{ij} \elmASshort{ij}{ij} \equiv \Eref, \label[eq]{eq:theo:e0ref}
\end{align}
named the \textit{reference energy}. Commonly wicks theorem is applied to \cref{eq:theo:second_quant_ham} to pick out the \cref{eq:theo:e0ref} contribution, defining the \textit{normal ordered} Hamiltonian
\begin{align*}
    \ham &= \hamno + \Eref = \fockno + \interno + \Eref,
\end{align*}
where $\fockno$ and $\interno$ is the normal ordered \textit{Fock operator} and two body interaction respectively.
\begin{align}
    \fockno &= \sum_{pq} \fshort{p}{q} \set{\crt{p} \ani{q}}, \label[eq]{eq:theo:fock_no} \\
    \interno &= \frac{1}{4}\sum_{pqrs} \elmASshort{pq}{rs} \set{\crt{p}\crt{q}\ani{s}\ani{r}}. \label[eq]{eq:theo:interaction_no}
\end{align}
The operators inside the curly brackets denotes \textit{normal ordering}. In constructing the Fock operator, the matrix elements $\fshort{p}{q}$ are given as 
\begin{align*}
    \fshort{p}{q} = \hshort{p}{q} + \sum_i \elmASshort{pi}{qi}
\end{align*}
One major reason for doing this is the applicability of the \textit{Generalized Wicks Theorem} (GWT), such that we only need to consider contractions between different normal ordered strings \citep{ferialdiGeneralWickTheorem2021}.

\begin{align}
    \hat{H}\ket{\Psi} = E \ket{\Psi} \label[eq]{eq:theo:schroding_equation}
\end{align}

\subsection{Hartree-Fock}\label[sec]{sec:theo:hartreefock}
The Hartree-Fock method is one of the cheapest and most commonly applicated many-body methods. Using the reference energy equation \cref{eq:theo:e0ref}, we perform a basis change to the Hartree-Fock basis, based on minimizing the ansatz expectation value. Using Greek letters to index the computational basis $\alpha, \beta \ldots$, going over all states $L$ we can change to the Hartree-Fock basis using

\begin{align*}
    \ket{i} = \sum_{\alpha} C_{\alpha i}\ket{\alpha}
\end{align*}
where $C_{\alpha i}$ are the basis coefficients. These are the objects used for the parameter search in configuration space. We are however not free to choose an arbitrary transformation, since we require the Hartree-Fock states to be orthogonal $\braket{i}{j} = \delta_{ij}$. We formulate this constraint as a function of the coefficients $C$ 

\begin{align*}
    \mathcal{G}(C) &= \sum_{ij} \epsilon_{ij} (\delta_{ij} - \ip{i}{j}) \\
                    &= \sum_{ij}\sum_{\alpha\beta} \epsilon_{ij} (\delta_{ij} - C^*_{\alpha i} C_{\beta j} \ip{\alpha}{\beta}) = 0,
\end{align*}
where $\epsilon_{ij}$ as the Lagrange multipliers. The goal is minimizing 

\begin{align*}
    \mathcal{E}(C) &= \braansatz \ham \ketansatz = \sum_{i} \sum_{\alpha\beta} C_{\alpha i}^* C_{\beta i} \hshort{\alpha}{\beta} \\
    &+ \frac{1}{2}\sum_{ij}\sum_{\alpha\beta\gamma\delta} C_{\alpha i}^* C_{\beta j}^* C_{\gamma i} C_{\delta j} \elmASshort{\alpha \beta}{\gamma \delta}
\end{align*}
and thus the relevant Lagrangian then becomes

\begin{align*}
    \mathcal{L}(C) = \mathcal{E}(C) + \mathcal{G}(C).
\end{align*}
The equation to solve are then found by considering a stationary point of the Lagrangian $\delta \mathcal{L} = 0$ wrt. the coefficients $C$. Performing this minimization, we achieve an eigenvalue problem with the matrix
\begin{align}
    \hamhf{\alpha\beta} = \hshort{\alpha}{\beta} + \sum_{\gamma\delta} \rho_{\gamma\delta} \elmASshort{\alpha\gamma}{\beta \delta}, \hspace{20px} \rho_{\gamma\delta} = \sum_i C^*_{\gamma i} C_{\delta i} \label[eq]{eq:theo:hartree_fock_matrix_and_density} 
\end{align}
having the coefficients as eigenvectors and the Lagrange multipliers as eigenvalues
\begin{align}
    \sum_{\beta} \hamhf{\alpha \beta} C_{i \beta} = \epsilon_i C_{i \alpha}. \label{eq:theo:hartreefock_eigenvalueproblem}
\end{align}
Where the Lagrange multipliers are diagonal since by their Hermiticity we can perform a unitary transformation to a basis where they are diagonal $\epsilon = U \epsilon' U^\dagger$. In addition, the matrix $\rho_{\gamma \delta}$ can be interpreted as the density matrix.
 
\subsection{Coupled Cluster}
The exact solution $\ket{\Psi}$ is approximated by an exponential ansatz $\ketCC$ 
\begin{align}
    \ket{\Psi} \approx \ketCC \equiv \exp{\cluster{}} \ketansatz. \label[eq]{eq:theo:exponential_ansatz}
\end{align}
The operators $\cluster{} = \cluster{1} + \cluster{2} + \ldots$ acting on the ground state ansatz $\ketansatz$ are the so-called \textit{cluster operators} defined as
\begin{align}
    \cluster{m} = \frac{1}{(m!)^2} \sum_{\substack{ab\ldots\\ij\ldots}} \amplitude{ab\ldots}{ij\ldots} \set{\crt{a}\ani{i} \crt{b} \ani{j}\ldots} \label[eq]{eq:theo:cluster_operators_general}
\end{align}
where $m \leq N$. The scalars $\amplitude{ab\ldots}{ij\ldots}$ are unknown expansion coefficients called \textit{amplitudes}, which we need to solve for. All the creation and annihilation operators of \cref{eq:theo:cluster_operators_general} anticommute, giving the restriction that

\begin{align}
    \amplitude{\hat{P}(ab\ldots)}{\hat{P}'(ij\ldots)} = (-1)^{\sigma(\hat{P})+\sigma(\hat{P}')} \amplitude{ab\ldots}{ij\ldots}. \label[eq]{eq:theo:amplitude_permutation_symmetry}
\end{align}
Here $P$ and $P'$ permutes $\sigma(P)$ and $\sigma(P')$ indices respectively. This is the reason for the prefactor of \cref{eq:theo:cluster_operators_general}, since we have $m!$ ways to independently permute particle and hole indices. Instead of having $(L-N)^m N^m$ independent unknowns, we reduce this number by a factor of $(m!)^{2}$. 

\subsection{Doubles Truncation}
Considering $N$ cluster operators in the exponential ansatz of \cref{eq:theo:exponential_ansatz} is not computationally feasible for realistic systems. The common practice is to include one or more $\cluster{m}$ operators, making a truncation on $\ketCC$ as well. In the following we will include only the double excitation operator $\cluster{2}$, know as the CCD approximation. This gives us 
\begin{align}
    \ket{\Psi} &\approx \ketCC \approx \ketCCD \equiv \exp{\cluster{2}} \ketansatz \label[eq]{eq:theo:CCD_exponential_ansatz}, \\
    \cluster{2} &= \frac{1}{4}\sum_{abij} \amplitude{ab}{ij}\set{ \crt{a} \ani{i} \crt{b}\ani{j}} \label[eq]{eq:theo:CCD_cluster},
\end{align}
with the four-fold amplitude permutation symmetry following from the CAR \footnote{For double amplitudes, the index permutation symmetry is equal to that of antisymmetrized two-body matrix elements $\elmAS{pq}{rs}$ from \cref{eq:theo:matrix_elements_symmetry_AS}.},
\begin{align}
    \amplitude{ab}{ij} = - \amplitude{ba}{ij} = - \amplitude{ab}{ji} = \amplitude{ba}{ji}. \label[eq]{eq:theo:CCD_amplitude_symmetry}
\end{align}
Incorporating the CCD approximation in the Schr\"odinger equation (\cref{eq:theo:schroding_equation}), we see that
\begin{align}
    \ham \exp{\cluster{2}} \ketansatz &= E \exp{\cluster{2}} \nonumber \ketansatz,  \\
    \hamno \exp{\cluster{2}} \ketansatz &= \DECCD \exp{\cluster{2}} \ketansatz, \label[eq]{eq:theo:schroding_equation_CCD}
\end{align}
where $\DECCD = E-\Eref$. Expanding both sides and taking the inner product with $\braansatz$, we in principle get an equation for the energy. However, this approach is not amenable to practical computer implementation \citep{bartlettCoupledClusterMethodsMolecular1984} since the amplitude equation will be coupled with the energy equation. Therefor, we rather apply a similarity transform to \cref{eq:theo:schroding_equation_CCD} by multiplying by the inverse of $\exp{\cluster{2}}$,
\begin{align}
    \exp{-\cluster{2}} \hamno \exp{-\cluster{2}} \ketansatz &= \DECCD \ketansatz \nonumber \\
    \simham \ketansatz &= \DECCD \ketansatz \label[eq]{eq:theo:ccd_eigenvalueproblem}
\end{align}
where $\simham = \exp{-\cluster{2}} \hamno \exp{-\cluster{2}}$ is the similarity transformed Hamiltonian. Using this reformulated eigenvalue problem, we can perform the inner product with different states to calculate both $\DECCD$ and $\amplitude{ab}{ij}$. Considering $\braansatz$ we get

\begin{align}
    \braansatz \simham \ketansatz = \DECCD, \label[eq]{eq:theo:energy_equation_sim_transformed}
\end{align}
named the \textit{energy equation}. Considering excited states, we arrive at the \textit{amplitude equations}
\begin{align}
    \braexed{ab\ldots}{ij\ldots} \simham \ketansatz \label[eq]{eq:theo:amplitude_equations},
\end{align}
used for finding the unknown amplitudes $\amplitude{ab}{ij}$. To find explicit expressions for \cref{eq:theo:energy_equation_sim_transformed} and \cref{eq:theo:amplitude_equations}, we expand $\simham$ using the Hausdorff expansion
\begin{align}
    \simham &= \hamno + \commutator{\hamno}{\cluster{2}} + \frac{1}{2!}\commutator{\commutator{\hamno}{\cluster{2}}}{\cluster{2}}. \label[eq]{eq:theo:ham_commutator_expansion}
\end{align}
The truncation at the two-fold commutator comes from the fact that we have a two-body interaction combined with $\cluster{2}$ only performing double excitations. When evaluated with a doubly excited state, at least one creation or annihilation operator from each of the cluster operators has to be contracted with $\hamno$. Therefor having eight creation and annihilation operators in two $\cluster{2}$, four of them can be contracted with the four from $\hamno$, while the other four with the operators from $\braexed{ab}{ij}$. This gives the CCD amplitude equation calculated from 

\begin{align}
    \braexed{ab}{ij}\simham\ketansatz = 0 \label[eq]{eq:theo:amplitude_equation_CCD}
\end{align}
The calculations can be further simplified from \cref{eq:theo:ham_commutator_expansion}, noting that any creation operator $\crt{a}$ or annihilation operator $\ani{i}$ to the left of $\hamno$ can not give any non-zero contractions due to the lack of a $\ani{a}$ or $\crt{i}$ to its left. Therefor we only get contribution from fully contracted $\hamno$, $\hamno \cluster{2}$ and $\hamno \cluster{2}\cluster{2}$ terms, where each $\cluster{2}$ has at least one leg in $\hamno$.  

To make practical use of \cref{eq:theo:energy_equation_sim_transformed} and \cref{eq:theo:amplitude_equation_CCD}, a chain of contractions applying the GWT has to be performed. This is a tedious task, thus all amplitude and energy equations here has been calculated using \verb|Drudge| \footnote{Drudge / Gristmill, Symbolic tensor and non-commutative algebra with powerful automatic code generation and optimization, written by Jinmo Zhao and Gustavo E Scuseria, \url{https://tschijnmo.github.io/drudge/}}. The energy equation becomes

\begin{align}
    \DECCD = \frac{1}{4} \sum_{abij} \elmASshort{ij}{ab} \amplitude{ab}{ij} \label[eq]{eq:theo:Energy_CCD_explicit},
\end{align}
with the amplitude equation in its pure glory (using Einstein summation convention)

\begin{align}
    \begin{split}
        &\elmASshort{ab}{ij} + \permoperator{ab} \fshort{b}{c} \amplitude{ac}{ij} - \permoperator{ij} \fshort{k}{j} \amplitude{ab}{ik} \\
        &+ \frac{1}{2} \elmASshort{ab}{cd} \amplitude{cd}{ij} + \frac{1}{2} \elmASshort{kl}{ij} \amplitude{ab}{kl} + \permoperator{ab} \permoperator{ij}\elmASshort{kb}{cj} \amplitude{ac}{ik} \\
        &+ \frac{1}{4}\elmASshort{kl}{cd} \amplitude{cd}{ij} \amplitude{ab}{kl} + \permoperator{ij} \elmASshort{kl}{cd} \amplitude{ac}{ik} \amplitude{bd}{jl} \\
        &- \frac{1}{2} \permoperator{ij} \elmASshort{kl}{cd} \amplitude{dc}{ik} \amplitude{ab}{lj} - \frac{1}{2} \permoperator{ab} \elmASshort{kl}{cd} \amplitude{ac}{lk} \amplitude{db}{lj} = 0.
    \end{split}\label[eq]{eq:theo:Amplitude_CCD_explicit}
\end{align}
Here we have defined permutation operators $\permoperator{pq} = 1 - \permoperatorshort{pq}$, where $\permoperatorshort{pq}$ interchanges the two indices $p$ and $q$.